Reducing object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-09 paper/response_2022.tex

\section{Recommendation R2: RQ - Review Again After Major Changes}

\textbf{Comments:}The paper has greatly improved with the new focus! I would like to thank the authors for the extra work. I do have a few remaining comments:\\

\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use standard metrics for comparison, instead of the custom metrics currently used. For SSIM, reporting with the standard weightings is important (if the authors want, of course they can show both the standard weightings and the custom ones!). For RSME, I don't understand why the authors rescale images before computing the metric -- this can greatly alter the metrics, making them difficult to interpret and compare across papers. For the RMSE, it is best to not use any scaling at all (or, a fixed scaling for all reconstructions only based on the ground truth).
}}\\

\textbf{Response}:
Since SSIM inherently offers a flexibility to set coefficients based on what we want to evaluate, we believe that having a set of coefficients that focus on measuring structural preservation is better suited for our goal. However, in the paper, we have now included quantitative results with both custom (structure-focussed) SSIM and default SSIM. The benefit of the proposed method is seen with either setting of the metric.

For computation of both SSIM and RMSE, we find that rescaling is necessary because different optimization routines generate solutions whose intensity ranges vary from that of the ground truth. For example, for reconstruction of the potato data from 18 views, Table~\ref{Tab:ranges} shows the min. and max. intensity values of the groundtruth and reconstructed volumes.\\

\begin{table}[]
  \centering
  \caption{Minimum and maximum intensity values of groundtruth and reconstructed volumes of potato data, reconstructed from 18 views.}
  \begin{tabular}{|l|l|l|l|}
\hline
 & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
\textbf{Min.} & 0.00 & -0.19 & 0.00 \\ \hline
\textbf{Max.} & 1.00 & 0.24 & 0.24 \\ \hline
  \end{tabular}
  \label{Tab:ranges}
\end{table}

### 2022-02-10 paper/response_2022.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Author Response to Reviewers for the paper `Reducing object prior-bias in sparse projection tomographic reconstructions'}
\begin{document}
\maketitle

We thank all the reviewers for their detailed feedback on our
work. Based on their comments, we have incorporated significant
changes in our revised paper, and have discussed these in this
document. We also request the reviewers to read these comments along
with the changes in the paper, especially related the comments in
Section~6 (Results).

@@

\section{Comments from AE}

\textcolor{blue}{\textit{While the reviewers have acknowledged
    improvements compared to the earlier manuscript, they have raised
    some important concerns about the manuscript in its current
    form. While addressing each of the reviewer specific comments,
    please pay specific attention to the following:}}

  \begin{itemize}
  \item \textcolor{blue}{\textit{Characterization of deep learning
        methods and its relation to the presented work}}

    We have now included a discussion of deep-learning (DL) methods in
    `Related Work', Section 2, of our paper, and have cited a few
    notable references pertaining to training neural networks to
    directly predict full-view sinogram and reconstruct the test
    object from its limited-view measurements. The ability of DL to
    uncover new features from one or many example images or training
    session is not being disputed. Here the focus is on a new discrete
    algorithm that builds structural maps that can and does point to
    new features.

@@

    \item\textcolor{blue}{\textit{Presenting all relevant details so
          the work in the paper can be re-produced without ambiguity}}

      To ensure reproducibility, we had earlier shared the code files
      for 2D reconstructions. We have now added complete code for 3D
      reconstructions as well, and as suggested, placed them in our
      github repository:
      \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}
      This repository is currently not a public repository since the
      paper is in the review process.

@@

  \end{itemize}

As a side note, based on the suggestion of R3, we have made a
slight change to the title of the paper using the word ``Mitigating''
instead of ``Eliminating''.

@@

  \section{Recommendation R1: AQ - Publish With Minor, Required
    Changes}

  \textbf{Comments:}The authors have significantly improved their
  paper when compared to the earlier rejected submission. The results
  are now much clearer. I have a few relatively minor comments below.

  \textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:}\textit{In
      the abstract, I feel you are underselling your
      contributions. You may want to add a line or two that quantifies
      the fidelity of your reconstructions for a given percentage of
      the total number of views (as required by Nyquist
      sampling). Your method is very relevant for scenarios such as
      Flash X-ray CT where we only are able to measure 5-20
      views. Hence, some quantifying statement that appeals to the
      very few view CT community may be useful. In the abstract, the
      sentence "In this work, we mitigate this problem by first
      estimating the location of new regions and then imposing
      object-prior in only old regions which are similar to the
      prior." introduces terms such as "new regions" and "old regions"
      that don't carry any meaning. Please rewrite.}}\\

  \textbf{Response:}

  Duly noted the issue of ``old-regions'', we have defined and
  re-written the  abstract.

  While we appreciate the suggestion on the quantification of our
  results, we felt that (as styles go) it would be better to keep a
  lower profile because of the dependency on various factors such as
  the number of views and structural complexity of the object data
  itself.

  \textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53
      right column, you mention that your code will be
      released. However, I recommend including a link to github or
      other website with the code before publication.}}

  \textbf{Response:} Earlier, we had shared the complete code for 2D
  reconstruction. We have now added code for 3D reconstructions as
  well in the github repository:
  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}

  \textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42
      left column, what are the weights for? I don't see any equation
      where these can be substituted for quantifying results. Also,
      RMSE and SSIM have their own definitions.}}

  \textbf{Response:} This point has come up in R2 as well (in a larger
  context), and we defer the discussion to that response.  Our earlier
  usage of the term `weights' with respect to SSIM might have been
  confusing since we also refer to `weights-map' throughout our paper.

@@

As far as the stability of parameter $k$ is concerned, in Fig. 8 of our paper, we show how the quality of reconstructions vary for different values of $k$. We see that the reconstructions are similar for a significant range of $k$ values. (5-40) for Okra. For the purposes of demonstrating the benefit of our method, we choose $k$ omnisciently assuming known ground truth of test (and unknown RoI). In real-world, $k$ must also be tuned by using one of the templates as pseudo-test and performing a grid search to select the best value.\\

\section{Recommendation R2: RQ - Review Again After Major Changes}

\textbf{Comments:}The paper has greatly improved with the new focus! I would like to thank the authors for the extra work. I do have a few remaining comments:\\

\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use
    standard metrics for comparison, instead of the custom metrics
    currently used. For SSIM, reporting with the standard weightings
    is important (if the authors want, of course they can show both
    the standard weightings and the custom ones!). For RSME, I don't
    understand why the authors rescale images before computing the
    metric -- this can greatly alter the metrics, making them
    difficult to interpret and compare across papers. For the RMSE, it
    is best to not use any scaling at all (or, a fixed scaling for all
    reconstructions only based on the ground truth).  }}

\textbf{Response}:

\begin{enumerate}

  \item

    [Meta comment: This section is also in response to R1 (\emph{SSIM
      have their own definitions}.]

    [Standard vs custom:] We have used the commonly used SSIM metric,
    for which, we have now provided reference to the original paper
    where the metric has been defined. As is well know, SSIM comprises
    of three factors: Luminance, Contrast and Structure. These factors
    (now termed `coefficients', earlier `weights' paper) for these
    three terms are adjustable to suit the application at hand.  Since
    SSIM inherently offers a flexibility to set coefficients based on
    what we want to evaluate, we believe that having a set of
    coefficients that focus on measuring structural preservation is
    better suited for our goal.

    However, in the revised version, we have now included quantitative
    results with both custom (structure-focussed) SSIM and default
    SSIM. The benefit of the proposed method is seen with
    \textbf{either} setting of the metric.

    Since the discussion on SSIM has persisted from the previous
    version, we take the liberty of providing a more detailed
    response. % A description of
    % computation of SSIM for a 2D image is given below. (The same
    % formula can be extended to 3D.)

where $n$ denotes the total number of pixels. The coefficients
$\alpha$, $\beta$ and $\gamma$ are set to $1$ as default, but need to
be adjusted to suit the application goal.

\item Rescaling

  For computation of both SSIM and RMSE, we find that rescaling is
  necessary because the different optimization routines generate
  solutions whose ranges vary from that of the ground truth.  For
  example, for reconstruction of the potato data from 18 views,
  Table~\ref{Tab:ranges} shows the minimum and maximum intensity
  values of the groundtruth and reconstructed volumes (in the case of
  TV regularization). The pernicious effect of this is obviously
  invisible in the qualitative results where the display program
  autoadjusts showing TV superior to FDK. In a quantitative setting it
  becomes necessary to rescale, otherwise TV using a prior will appear
  to be inferior to FDK (without a prior).  The same issue persists in
  the reconstruction using the external optimization program
  mentioned. %TODO give section or reference?

\begin{table}[]
  \centering
  \caption{Minimum and maximum intensity values of groundtruth and
    reconstructed volumes of potato data reconstructed from 18
    views.}
  \begin{tabular}{|l|l|l|l|}
\hline
 & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
\textbf{Minimum} & 0.00 & -0.19 & 0.00 \\ \hline
\textbf{Maximum} & 1.00 & 0.24 & 0.24 \\ \hline
  \end{tabular}
  \label{Tab:ranges}
\end{table}
\end{enumerate}

\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is
    not very convincing to me. In practice, given a certain number of
    projections, a user might want to compare possible reconstruction
    algorithms to decide what is the best one to use from a
    computation time / reconstruction quality tradeoff point of
    view. Therefore, it would be good to compare times between methods
    for the same number of projections (it is of course possible to
    show results for a few different cases, e.g. many views, moderate
    views, and few views). It is also useful to include more detailed
    information about the data size (detector size, reconstruction
    size, number of projections, etcetera). Furthermore, please show
    timing results for all steps of the algorithm, including the
    computation of the low quality reconstructions, pilot
    reconstructions, and building of eigenspaces.}}

\textbf{Response}:

\begin{enumerate}

\item \emph{ \ldots therefore it would be good \ldots } Indeed, this
  is precisely what we have done.  Sadly our column header of Table-6
  conveyed a different impression. We intended to indicate that FDK is
  good for sufficient views, and TV is sufficent for moderate
  views. We ended up misleading the reviewer.

  Hence, we have edited the caption and Table-field titles of Table-6
  (Page 10) to accurately describe details of measurement.

\item \emph{ \ldots all steps \ldots} We also provide the details
  required.  We note that the TV reconstruction \emph{is} our pilot
  reconstruction and hence the computation times are equal.

  Having specified the exact compute times in our machine, we also
  note that the type of machine and the degree of parallelism
  available in the current times make these timing measurements,
  especially for iterative solutions, subjective.

\end{enumerate}

\begin{figure}[!t]
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.186\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption[Okra 3D dataset]{Okra 3D dataset: One slice each from
       the templates (the 
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:templates_test_okra}
\end{figure}
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/fdk_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
\caption[3D reconstruction of okra dataset]{3D reconstruction of the okra from $10\%$ projection
  views (b) has strong streak artefacts, (c) blurred, (d) no new
  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
  corresponding to red and green regions) while simultaneously
  reducing streak artefacts.}
\label{fig:okra_3D_results}
\end{figure}

@@

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/fdk_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
\caption[3D reconstruction of okra dataset]{3D reconstruction of the okra from $10\%$ projection
  views (b) has strong streak artefacts, (c) blurred, (d) no new
  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
  corresponding to red and green regions) while simultaneously
  reducing streak artefacts.}
\label{fig:okra_3D_results}
\end{figure}

%--------------------------------------zoomed okra

\begin{figure}[!b]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
\caption[Zoomed results of Okra dataset]{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities).}
\label{fig:okra_zoomed_3D_results}
\end{figure}

\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the
    paper, the authors claim that existing object-prior based methods
    have problems, e.g.: "A common problem with these techniques is
    the strong influence of object-priors in the reconstruction of new
    regions in the test". At the moment, this hard claim is not
    supported in the paper by references or (even better) comparison
    results. It would be good to show, on one (or more) of the
    datasets used, that this is indeed the case, and that the proposed
    methods solves this problem.}}

\textbf{Response:} We have now included a reference (Pg.2, Line 3
under Sec.1-A) to a PhD thesis wherein the problem of object-priors
biasing the reconstruction of new test regions is discussed in detail.
A sample result (Fig.1-3 here) from the thesis is shown below. It
illustrates how an unweighted application of prior can adversely
affect the reconstruction of new regions in the test.

### 2022-02-13 paper/post_tci.tex
Removed brackets for RMSE in tables

We observe
that our method reconstructs new structures while simultaneously
reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
the reconstructed new regions using various methods. 
%The ground truth and reconstructions are normalized to lie in [0-1].
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
\label{fig:potato_zoomed_2D_results}
\end{figure}
\end{comment}
%-------------------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed potato from various
    methods. 
%The SSIM of ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:potato_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.22, 0.52 (0.36)
& 0.86, 0.92 (0.06) & \textcolor{red}{0.95, 0.97 (0.03)} \\ \hline \textbf{3D} & 0.30, 0.58 (0.26) & 0.56, 0.75 (0.21) & \textcolor{red}{0.72, 0.84 (0.16)}
\\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed okra from various
    methods. 
%SSIM of the ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The 2D reconstructed images are shown in Fig.~\ref{fig:okra_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.26, 0.46 (0.28)
& 0.27, 0.50 (0.24) & \textcolor{red}{0.56, 0.74 (0.15)} \\ 
\hline \textbf{3D} & 0.52, 0.65 (0.22) & 0.56, 0.70 (0.21) & \textcolor{red}{0.57, 0.71 (0.19)}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
%For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The  reconstructed images are shown in Fig.~\ref{fig:tmh_2D_results},}
\begin{tabular}{|l|c|c|c|c|}
\hline \textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline 0.54, 0.73 (0.04)
& 0.80, 0.91 (0.09) & \textcolor{red}{0.90, 0.95 (0.03)} \\ \hline 
\end{tabular}
\label{table:tmh_ssim}
\end{table}
%-----------------------------------------------------------------

@@

%----------------------------------------------------
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
\label{fig:sprouts_zoomed_2D_results}
\end{figure}
\end{comment}
%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed sprouts from various
    methods. 
%The SSIM of ideal reconstruction) is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:sprouts_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
 \\ \hline \textbf{2D} & 0.42, 0.67 (0.24)
& 0.61, 0.82 (0.17) & \textcolor{red}{0.72, 0.86 (0.13)} \\ \hline \textbf{3D} & 0.44, 0.67 (0.25) & 0.47, 0.73 (0.23) & \textcolor{red}{0.66, 0.82 (0.14)}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

>>>>

We observe
that our method reconstructs new structures while simultaneously
reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
the reconstructed new regions using various methods. 
%The ground truth and reconstructions are normalized to lie in [0-1].
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
\label{fig:potato_zoomed_2D_results}
\end{figure}
\end{comment}
%-------------------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of reconstructed potato from various
    methods. 
%The SSIM of ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:potato_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.22, 0.52, 0.36
& 0.86, 0.92, 0.06 & \textcolor{red}{0.95, 0.97, 0.03} \\ \hline \textbf{3D} & 0.30, 0.58, 0.26 & 0.56, 0.75, 0.21 & \textcolor{red}{0.72, 0.84, 0.16}
\\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of reconstructed okra from various
    methods. 
%SSIM of the ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The 2D reconstructed images are shown in Fig.~\ref{fig:okra_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.26, 0.46, 0.28
& 0.27, 0.50, 0.24 & \textcolor{red}{0.56, 0.74, 0.15} \\ 
\hline \textbf{3D} & 0.52, 0.65, 0.22 & 0.56, 0.70, 0.21 & \textcolor{red}{0.57, 0.71, 0.19}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
%For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The  reconstructed images are shown in Fig.~\ref{fig:tmh_2D_results},}
\begin{tabular}{|l|c|c|c|c|}
\hline \textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline 0.54, 0.73, 0.04
& 0.80, 0.91, 0.09 & \textcolor{red}{0.90, 0.95, 0.03} \\ \hline 
\end{tabular}
\label{table:tmh_ssim}
\end{table}
%-----------------------------------------------------------------

@@

%----------------------------------------------------
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
\label{fig:sprouts_zoomed_2D_results}
\end{figure}
\end{comment}
%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of reconstructed sprouts from various
    methods. 
%The SSIM of ideal reconstruction) is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:sprouts_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
 \\ \hline \textbf{2D} & 0.42, 0.67, 0.24
& 0.61, 0.82, 0.17 & \textcolor{red}{0.72, 0.86, 0.13} \\ \hline \textbf{3D} & 0.44, 0.67, 0.25 & 0.47, 0.73, 0.23 & \textcolor{red}{0.66, 0.82, 0.14}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}
